%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{comment} % used for commenting out multiple lines


\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Vitesh} % Your first name
\familyname{Krishna} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{Fernvale Link, Blk 467A, \#05-501}{Singapore (791467)}
\mobile{91543345}
\email{vilighter@gmail.com}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example


%\photo[70pt][0.4pt]{picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
\quote{}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2017--2018}{Master of Science in Nuclear Science \& Technology, (Reactor Technology track)}{University of Manchester}{The United Kingdom}{}{}

\cvitem{Modules completed include}{\textbf{Radiation \& Radiological Protection} \newline \textbf{Reactor Materials \& Lifetime behaviour} \newline \textbf{Nuclear Fuel Cycle} \newline \textbf{Radiological Environmental Impact Assessment}  \newline \textbf{Reactor Physics, Criticality \& Design}}

\cventry{2013--2016}{Bachelor of Science in Liberal Arts \& Sciences, (Concentration in Physics)}{Maastricht University}{The Netherlands}{\textit{GPA -- 7.9}}{\textbf{Upper Second Class Honours}}

\cvitem{Modules completed include}{\textbf{Nuclear \& Elementary Particle Physics} \newline \textbf{Quantum Mechanics} \newline \textbf{Quantum theory} \newline \textbf{Relativistic Electrodynamics} \newline *for full list of modules, please refer to Degree Transcript} \vspace{10pt}

 % Arguments not required can be left empty

\cventry{2007--2010}{Diploma in Chemical Engineering}{Temasek Polytechnic}{Singapore}{}{Specialized in Petrochemical}


\section{Publication}

\cvitem{}{\textbf{\emph{Krishna,Vitesh \& Yap, Ching \& Xiao, Sicong (2020). Assembly design of a Fluoride salt-cooled high temperature commercial-scale reactor: Neutronics evaluation and parametric analysis. Annals of Nuclear Energy. 141. 107288.10.1016/j.anucene.2019.107288.}}}

\section{Master Thesis}

\cvitem{Title}{\textbf{\emph{Core life extension of the SMART reactor for applicability in marine propulsion }}}
\cvitem{Supervisors}{Professor Timothy Abrams \& Ms Olga Negri}
\cvitem{Description}{This study involved in developing a reactor core and extending the core life for cargo ships such that the refuelling frequency is reduced, whilst maintaining acceptable reactivity swing.}




\section{Bachelor Thesis}

\cvitem{Title}{\textbf{\emph{Optimizing the search strategy of microscopic black holes using the ATLAS detector at a center-of-mass-energy of $\sqrt[]{s} = 13 TeV$}}}
\cvitem{Supervisors}{Associate Professor Dr. Ronald Westra \& Dr. Sarah Williams}
\cvitem{Description}{This thesis was conducted in conjunction with CERN, the European Organization for Nuclear Research. The thesis investigated possibilities to further optimize the existing search strategy of microscopic black holes. At the end of my research, I developed a variable that was proven to be more sensitive than the existing variable used at ATLAS, CERN. I proposed my variable for future experiments at ATLAS involving microscopic black holes.}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\subsection{Vocational}

%------------------------------------------------

\cventry{Jun-Sep 2009}{Polytechnic Internship}{\textsc{Vopak Terminals}}{Singapore}{}{Worked on waste water purification project involving microbial treatment. Also worked on project involving nitrogen padding in chemical storage tanks.}


\cventry{2010-2012}{National Service}{\textsc{MINDEF}}{Singapore}{}{Rank: Corporal \newline Conduct: Very Good \newline Performance: Very Good}

\cventry{Feb- Dec 2013}{Student Job}{\textsc{Maastricht University}}{The Netherlands}{}{Attending to queries brought up by prospective students. Promoting University to international students. Assisting with student admission related matters.}

\cventry{2017-Present}{Nuclear Researcher/Engineer}{\textsc{Singapore Nuclear Research and Safety Initiative (SNRSI)}}{Singapore}{}{Involved in nuclear safety research/studies and atmosheric dispersion research. Also involved in research related to GEN IV reactor. An active research member of the ASEAN network on Nuclear Power and Safety Research (ASEAN NPSR) }
%------------------------------------------------

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\cvitem{2017}{Singapore Nuclear Research and Safety Initiative Scholarship}
%\cvitem{2010}{Top Achiever Award -- Commerce}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}

\cvitem{Basic}{Java, Google Tag Manager, HTML}
\cvitem{Intermediate}{\textsc{python}, \textsc{C++}, linux (bash), ROOTCern}
\cvitem{Advanced}{\LaTeX, OpenOffice, MS Office, OpenFOAM, SERPENT}
%\cvitem{Advanced}{Computer Hardware and Support}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Conferences}

\cvitem{2019}{Asian MELCOR User Group Meeting, Daejeon, Republic of Korea}
\cvitem{2019}{Presented research findings at Annual ASEAN Nuclear Power Safety Research meet, Bangkok,Thailand}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{English}{First Language}{}
\cvitemwithcomment{Tamil}{Mothertongue}{}
%\cvitemwithcomment{Spanish}{Intermediate}{Conversationally fluent}
\cvitemwithcomment{Spanish}{Intermediate}{}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

%\section{Interests}

%\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

%\cvlistdoubleitem{Gaming}{Music}
%\cvlistdoubleitem{Soccer}{Programming}
%\cvlistitem{Traveling}

%----------------------------------------------------------------------------------------
%	Referees SECTION
%----------------------------------------------------------------------------------------

\section{Referees}

\cvitemwithcomment{Prof. Timothy Abrams}{tim.abram@manchester.ac.uk}{Professor, University of Manchester}

\cvitemwithcomment{Dr. Ronald Westra}{westra@maastrichtuniversity.nl}{Associate Professor Physics}
 
\cvitemwithcomment{Dr. Chris Pawley}{c.pawley@maastrichtuniversity.nl}{Physicist and materials scientist}



%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

\clearpage
\begin{comment}

\end{}
\recipient{}{} % Letter recipient
\date{\today} % Letter date
\opening{Dear Sir/Mdm,} % Opening greeting
\closing{Sincerely yours,} % Closing phrase
%\enclosure {}% List of enclosed documents

%\makelettertitle % Print letter title
I am writing to enquire about the above vacancy in your company. 

As seen from my CV, I have completed my bachelors degree with Maastricht University, an institution that places intense emphasis on Problem Based Learning (PBL). This method of learning has enabled me to work coherently with different types of people and sharpen my critical thinking abilities. 

I am a conscientious worker who is detailed-oriented. As a proactive learner, I jump at an opportunity to expand my knowledge and experiences from whomever it might be. Through my degree programme, I developed an interest in programming while improving my laboratory and numeracy skills.

If needed, I have excellent references who would be delighted to attend to your queries about my diligence. 

I will be exalted to discuss any other vacancies with you at your earliest convenience and will be available for an interview immediately. Please see attached for an enclosed a copy of my CV.

Looking forward to a favorable reply.



%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature
\end{comment}

%----------------------------------------------------------------------------------------

\end{document}